---
title: "Final demo code for CEW R shortcourse"
author: "Pepe Rodriguez"
date: "2022-10-02"
output: 
 html_document:
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Required packages

```{r}

library(tidyverse)  # Obviously!

library(here) # Helps with filepaths

library(lubridate) # asistance with dates

library(janitor) # helps cleaning variable names

```

# Loading the data

Letas load, one by one, the different data pieces that make our dataset

First we start with the site log

```{r}

site_log_original <- read_csv(here("data_raw", "site_log.csv"))

site_log_original

```

Now we read rge sample log

```{r}

sample_log_original <- read_csv(here("data_raw", "sample_log.csv"))

sample_log_original

```

And now, the analytical results

```{r}

analytical_results_original <- read_csv(here("data_raw", "analytical_results.csv"))

analytical_results_original

```

# Data processing

Now we perform any data processing that we consider necesary

Lets start with the sample log:

```{r}

sample_log <- sample_log_original %>% 
  mutate(date = (str_c(year, month, day, sep = "/"))) %>% 
  mutate(date = ymd(date))

sample_log

```

The variable name sin the analytical data do not follow the [Tidyvers style guide](https://style.tidyverse.org/index.html), so we are going to use the function `clean_names()` from the **{Lubridate}** package to help us

```{r}

analytical_results <- analytical_results_original %>% 
  clean_names()

analytical_results

```


# Combine all the data

```{r}

combined_data <- sample_log %>% 
  left_join(site_log_original) %>% 
  left_join(analytical_results)

combined_data

```


# Plot

And now we can make a nice temporal trend figure for each treatment


```{r}


combined_data %>% 
  ggplot() +
  facet_wrap(~treatment) +
  geom_point(aes(x = date, y = parameter_a_mg_l)) +
  theme_bw()
  
  

```












